Playing multiple games using deep reinforcement learning, or Spatial Attention network can play (beat) simultaneously multiple games in reinforcement learning

### 2019-09-15 multi_dqn_paper/paper.tex
common

@@

>>>>

Some recent work in attention RL can be found in :\cite{bib:rl_attention_multi_focus} \cite{bib:rl_attention} \cite{bib:rl_attention_multi_view}.

@@

\bibitem{bib:rl_attention_multi_focus}
Multi-focus Attention Network for Efficient Deep Reinforcement Learning.
Jinyoung Choi, Beom-Jin Lee, Byoung-Tak Zhang, 2017 \url{https://arxiv.org/abs/1712.04603}

\bibitem{bib:rl_attention}
Reinforcement Learning with Attention that Works: A Self-Supervised Approach.
Anthony Manchin, Ehsan Abbasnejad, Anton van den Hengel, 2019, \url{https://arxiv.org/abs/1904.03367}

\bibitem{bib:rl_attention_multi_view}
Attention-based Deep Reinforcement Learning for Multi-view Environments.
Elaheh Barati, Xuewen Chen, Zichun Zhong, 2019 \url{https://arxiv.org/abs/1905.03985}
